### 2015-06-26 reports/paper/introduction.tex
add
update

In this work, we have built a source localization system that is portable, inexpensive, yet reasonably accurate for localization in a small area. To test the accuracy of our localization system, we perform acoustic localization experiments in an one meter by one meter area. The experiment area size is adequate for our purposes because human arm movement will generally be constrained in this area. Our experiment show that our system localizes both static and moving acoustic source with good accuracy in this area. Our system is built with inexpensive electret microphones mounted on portable frames. Users can interact with our system using any device that has audio output such as a mobile phone.

@@

\section{Contribution}
In this thesis, we provided a detailed simulation analyzing the impact of the arriving time estimation accuracy on localization error. We evaluated different array architectures, and showed that a two array architecture achieves good localization accuracy while maintaining good portability. We implemented and built the proposed sound localization system and compared different state of the art methods for localization and tracking. We also demonstrated that our system can be used as a tool for painting in space.
In this thesis, we first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.

>>>>

In this work, we have built a source localization system that is portable, inexpensive, yet reasonably accurate for localization in a small area. The purpose of our system is to give applications to designs that allow remote human computer interaction. To test the accuracy of our localization system, we perform acoustic localization experiments in an one meter by one meter area. The experiment area size is adequate for our purposes because human arm movement will generally be constrained in this area. Our experiment show that our system localizes both static and moving acoustic source with good accuracy in this area. Our system is built with inexpensive electret microphones mounted on portable frames. Users can interact with our system using any device that has audio output such as a mobile phone.

@@

\section{Contribution}
In this thesis, we provided a detailed simulation analyzing the impact of the arriving time estimation accuracy on localization error. We evaluated different array architectures, and showed that a two array architecture achieves good localization accuracy while maintaining good portability. We implemented and built the proposed sound localization system and compared different state of the art methods for localization and tracking. We also demonstrated that our system can be used as a tool for painting in space.

We first discussed in Chapter II some prior relevant research and approaches in sound localization. In Chapter III, we evaluated different array architectures and their impact on localization accuracy. We demonstrated that a two array system outperforms a single array system of similar physical dimension. In Chapter IV, we first presented the chosen architecture along with hardware details, followed by experiment details and results.

### 2015-06-26 reports/paper/prior_movement.tex
update

Note that by modeling up to acceleration, we are implicitly assuming higher order motion variables are constant (such as jerk). Kalman filter includes a process noise term $Q$ that can be used to partially reduce this effect, but there will exist systematic tracking bias if there is jerk change.

>>>>

Note that by modeling up to acceleration, we are implicitly assuming higher order motion variables are constant (such as jerk). This assumption gives the system a tracking bias if there is a jerk change. Kalman filter also includes a term $Q$ that can be used to model the process noise.
